Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-29 sattose/paper.tex
Small changes

There are many other publications that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, none of the publications describing a refactoring tool have published their source code or application for refactoring support. Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable. Furthermore, all of these tools only support a subset of all harmful clones that are found. Furthermore, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.

@@

From these results we can see, somewhat surprisingly, that the claim of 98\% of clones being produced at method-level is nowhere near correct. In fact, around 58\% of the clones are produced at method-level. About 39\% of clones either span several methods/constructors or contain something like a field declaration. Another 3\% of the clones is found in contructors. The amount of clones found in interfaces and enumerations is very low.

@@

@@

\subsubsection{Acknowledgements}
We would like to thank the Software Improvement Group (SIG) for their continuous support in this project.

>>>>

There are many other publications that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, none of the publications describing a refactoring tool have published their source code or application for refactoring support. Furthermore, all of these tools only support a subset of all harmful clones that are found. Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable. Finally, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.

@@

From these results we can see that the claim of 98\% of clones being produced at method-level is nowhere near correct. In fact, around 58\% of the clones are produced at method-level. About 39\% of clones either span several methods/constructors or contain something like a field declaration. Another 3\% of the clones is found in contructors. The amount of clones found in interfaces and enumerations is very low.

@@

The most trivial way to merge a clone is though method extraction. However, method extraction is not always possible.

@@

\section*{Acknowledgements}
We would like to thank the Software Improvement Group (SIG) for their continuous support in this project.
